# Seasonal SST Anomalies

**Description**: Seasonal SST Anomalies

**Indicator category**: Database pull with analysis

**Found in**: State of the Ecosystem - Gulf of Maine & Georges Bank (2018, 2019, 2020), State of the Ecosystem - Mid-Atlantic (2018, 2019, 2020)

**Contributor(s)**: Sean Hardison, Vincent Saba
  
**Data steward**: Kimberly Bastille, <kimberly.bastille@noaa.gov>
  
**Point of contact**: Kimberly Bastille, <kimberly.bastille@noaa.gov>
  
**Public availability statement**: Source data are available [here](https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).


test for rnaturalhires

### Plotting

```{r, code = readLines("https://raw.githubusercontent.com/NOAA-EDAB/ecodata/master/chunk-scripts/LTL.Rmd-seasonal-sst.R"), eval=TRUE, echo = FALSE,  fig.cap = "Caption."}
```

```{r rec-groups, eval = T, echo = F}

rec_spp <- read.csv(here::here("data","rec_spp_list.csv")) 
rec_spp %>% 
  dplyr::rename("Common Name" = "Common_Name", 
                "Scientific Name" = "Scientific_Name", 
                "Diversity Analysis" = "Diversity_analysis")

knitr::kable(rec_spp, caption="Species included in recreational catch diversity analysis.") %>%
  kableExtra::kable_styling(font_size = 8)
```