# Seasonal SST Anomalies

**Description**: Seasonal SST Anomalies

**Indicator category**: Database pull with analysis

**Found in**: State of the Ecosystem - Gulf of Maine & Georges Bank (2018, 2019, 2020), State of the Ecosystem - Mid-Atlantic (2018, 2019, 2020)

**Contributor(s)**: Sean Hardison, Vincent Saba
  
**Data steward**: Kimberly Bastille, <kimberly.bastille@noaa.gov>
  
**Point of contact**: Kimberly Bastille, <kimberly.bastille@noaa.gov>
  
**Public availability statement**: Source data are available [here](https://www.esrl.noaa.gov/psd/data/gridded/data.noaa.oisst.v2.highres.html).


test for rnaturalhires

### Plotting
```{r}
ne_epu_sf <- ecodata::epu_sf %>% 
  filter(EPU %in% c("GOM","GB"))

#Map line parameters
map.lwd <- 0.4

# Set lat/lon window for maps
xmin = -73
xmax = -65
ymin = 39
ymax = 45
xlims <- c(xmin, xmax)
ylims <- c(ymin, ymax)
sst <- ecodata::seasonal_sst_anomaly_gridded 

sst$Season <- factor(sst$Season, levels = c("Winter",
                                            "Spring",
                                            "Summer",
                                            "Fall"))

sst<- sst %>% mutate(Value = replace(Value, Value > 4, 4))
sst_map <- 
  ggplot() +
  geom_tile(data = sst, aes(x = Longitude, y = Latitude,fill = Value)) +
  geom_sf(data = ecodata::coast, size = map.lwd) +
  geom_sf(data = ne_epu_sf, fill = "transparent", size = map.lwd) +
  scale_fill_gradient2(name = "Temp.\nAnomaly (°C)",
                       low = scales::muted("blue"),
                       mid = "white",
                       high = scales::muted("red"),
                       limits = c(-4,4), 
                       labels = c("<-4", "-2", "0", "2", ">4")) +
  coord_sf(crs = crs, xlim = xlims, ylim = ylims) +
  facet_wrap(Season~.) +
  theme_map() +
  ggtitle("SST anomaly (2019)") +
  xlab("Longitude") +
  ylab("Latitude") +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.75),
        legend.key = element_blank(),
        axis.title = element_text(size = 11),
        strip.background = element_blank(),
        strip.text=element_text(hjust=0),
        axis.text = element_text(size = 8), 
        axis.title.y = element_text(angle = 90))


sst_map 

```
```{r , code = readLines("https://raw.githubusercontent.com/NOAA-EDAB/ecodata/master/chunk-scripts/LTL.Rmd-MAB-SST-insitu.R"), echo = F, fig.align="center", eval = F, ig.cap="MAB seasonal sea surface temperature time series overlaid onto 2019 seasonal spatial anomalies."}
 
```
